Void Correction Notes

### 2016-04-27 doc/void_correction.tex
Fixed small typo in trig identity.

Integrating over $d\theta^\prime$ and $d\phi^\prime$ and using the trig identity ${\cos(u)-\cos(v)=2\sin\left(\frac{u+v}{2}\right)\sin\left(\frac{u-v}{2}\right)}$ gives

>>>>

Integrating over $d\theta^\prime$ and $d\phi^\prime$ and using the trig identity ${\cos(u)-\cos(v)=-2\sin\left(\frac{u+v}{2}\right)\sin\left(\frac{u-v}{2}\right)}$ gives
